Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
add figure speedup MC

% \newcommand{\anytimeplot}[1]{
%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
% }
\newcommand{\anytimeplot}[1]{
  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
}

@@

>>>>

% \newcommand{\anytimeplot}[1]{
%   \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/knott-3d-300.data};              \addlegendentry{HC}
%   \addplot[color=black,mark=x] table[x=time,y=HC-CGC]{data3/knott-3d-300.data};          \addlegendentry{HC-CGC}
%   \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/knott-3d-300.data};               \addlegendentry{CGC}
%   \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/knott-3d-300.data};          \addlegendentry{KL}
%   \addplot[color=purple,mark=x] table[x=time, y=MCR-CCFDB]{data3/knott-3d-300.data};     \addlegendentry{MC-R}
%   \addplot[color=blue,mark=x] table[x=time, y=MCI-CCIFD]{data3/knott-3d-300.data};       \addlegendentry{MC-I}
%   \addplot[color=green,mark=x] table[x=time, y=DYNCC-HC-MC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-MC}
%   \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/knott-3d-300.data};    \addlegendentry{Fusion-HC-CGC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-MC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-MC}
%   \addplot[color=orange,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/knott-3d-300.data};  \addlegendentry{Fusion-WS-CGC}
% }
\newcommand{\anytimeplot}[1]{
  \addplot[color=brown,mark=x] table[x=time,y=HC]{data3/#1.data};              \addlegendentry{HC}
  \addplot[color=black,mark=square] table[x=time,y=HC-CGC]{data3/#1.data};          \addlegendentry{HC-CGC}
  \addplot[color=red,mark=x] table[x=time,y=CGC]{data3/#1.data};               \addlegendentry{CGC}
  \addplot[color=gray,mark=o] table[x=time, y=ogm-KL]{data3/#1.data};          \addlegendentry{KL} 
  \addplot[color=yellow!50!black,mark=square] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
  \addplot[color=purple,mark=o] table[x=time, y=MCR-CCFDB]{data3/#1.data};     \addlegendentry{MC-R}
  \addplot[color=blue,mark=o] table[x=time, y=MCI-CCIFD]{data3/#1.data};       \addlegendentry{MC-I}
  \addplot[color=green,mark=o] table[x=time, y=DYNCC-HC-MC]{data3/#1.data};    \addlegendentry{Fusion-HC-MC}
  \addplot[color=cyan,mark=x] table[x=time, y=DYNCC-HC-CGC]{data3/#1.data};    \addlegendentry{Fusion-HC-CGC}
  \addplot[color=orange,mark=o] table[x=time, y=DYNCC-WS-MC]{data3/#1.data};  \addlegendentry{Fusion-WS-MC}
  \addplot[color=pink,mark=x] table[x=time, y=DYNCC-WS-CGC]{data3/#1.data};  \addlegendentry{Fusion-WS-CGC}
}
%  \addplot[color=yellow!50!black,mark=o] table[x=time, y=ogm-mcfusion-HC-CF*]{data3/#1.data};  \addlegendentry{Fusion}
  %\addplot[color=green!50,mark=o] table[x=time, y=PIVOT*]{data3/#1.data};          \addlegendentry{PIVOT-BOEM}

@@

 \begin{figure}[ht]
    \centering
    \begin{tikzpicture}
    \begin{semilogxaxis}[  mark size=1pt,
   % restrict y to domain=-6000:-4400,
   %   restrict x to domain=10:4000,
    xlabel = {runtime},
    xmin = 0,
    xmax = 4100,
    legend to name = ledgendPositionMC,
    legend columns=4,
    width = 1.0\columnwidth,
    scaled ticks = false
    ] 
    \addplot[color=red,mark=x] table[x=time, y=MC-CCFDB-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-old}
    \addplot[color=orange,mark=o] table[x=time, y=MC-CCFDB-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCR-new}
    \addplot[color=blue,mark=x] table[x=time, y=MC-CCIFD-o*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-old}
    \addplot[color=cyan,mark=o] table[x=time, y=MC-CCIFD-n*]{data3/knott-3d-450b.data};          \addlegendentry{MCI-new}

    \end{semilogxaxis}
    \end{tikzpicture}
  \begin{center}
  \hypersetup{linkcolor = black}
  \ref{ledgendPositionMC}
  \hypersetup{linkcolor = red}
  \end{center}
    \caption{knott-3d-450b}\label{fig:at:knott-450b}
  \end{figure}
